---
title: "Initial Research"
author: "Fletcher Green"
date: "2026-03-31"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(alarmdata)
library(redist)
library(ggredist)
```

## Initial Research

- **Redistricting Status:**
  - Missouri: Governor Mike Kehoe signed new map into law on September 28, 2025.
  - New York: Litigation ongoing. Redistricting is not guaranteed.
  
- **Redistricting Reasoning:**
  - Missouri: Voluntarily redistricted.
  - New York: Redistricting potential due to litigation.
  
- **Source:**
  - <https://ballotpedia.org/Redistricting_in_New_York_ahead_of_the_2026_elections>

## Basic Missouri District Map

- I confirmed that I generated the correct map with this website: <https://www.zipdatamaps.com/politics/national/districts/map-of-missouri-congressional-districts>.

```{r init_missouri, echo=FALSE, warning=F}
map_mo <- alarm_50state_map('MO')
plans_mo <- alarm_50state_plans('MO')

map_mo |> 
  ggplot() +
  geom_district(aes(group = cd_2020, fill = ndv, denom = nrv + ndv)) +
  scale_fill_party_c() +
  theme_map()
```

## Basic New York District Map

- I confirmed that I generated the correct map with this website: <https://www.zipdatamaps.com/politics/national/districts/map-of-new-york-congressional-districts>.

- This appears to be be New York's current congressional boundaries. I need to do more research to figure out how to make a map of the proposed congressional boundaries. This is a comparison of the different boundaries that I found: <https://nyirc.gov/congressional-plan-2024>.

```{r init_ny, echo=FALSE, warning=F}
map_ny <- alarm_50state_map('NY')
plans_ny <- alarm_50state_plans('NY')

map_ny |> 
  ggplot() +
  geom_district(aes(group = cd_2020, fill = ndv, denom = nrv + ndv)) +
  scale_fill_party_c() +
  theme_map()
```

## Questions

- How can we create a system to efficiently compare different historical congressional boundaries in our states? Is such a system necessary for this project?

- What questions is our project trying to answer?